Using occupancy theory and Bayesian models to estimate otter populations in southeastern Minnesota

### 2010-03-01 Presentation/Presentation.tex
Added z-score boxplot.
added some slides

\begin{frame}[label=currentslide]{Independence, continued}

@@

\begin{frame}{Our model}
\end{frame}

\begin{frame}{Testing the model- data simulations}
\end{frame}

\begin{frame}{Modeling spatial correlation}
\end{frame}

\begin{frame}{Testing the CAR model}
\end{frame}

\end{document}

>>>>

\begin{frame}{Independence, continued}

@@

\begin{frame}{Bayesian vs. likelihood occupancy models}
	\begin{itemize}
		\item Maximum likelihood assumes random sample from large population
		\begin{itemize}
			\item Entire section of river was sampled
		\end{itemize}
		\item Most occupancy models have two random processes- occupancy and 
		detection
		\begin{itemize}
			\item We added false detection and track-laying
			\item Extra parameters made likelihood model complicated
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Issue with false detection}
	\begin{itemize}
		\item $(p=x, E=y, \psi=z)$ equivalent in terms of likelihood to 
		$(p=y,E=x,\psi=1-z)$.
		\item Leads to bimodal posterior distributions for $p$ and $E$.
		\item Solution: restrict $p$ to interval $(0.6,1)$, $E$ to interval 
		$(0,0.4)$.
	\end{itemize}
\end{frame}

%This slide for DNR only
\begin{frame}{Bayesian model specifics}
	\begin{itemize}
		\item $\psi,\theta \sim \text{Uniform}(0,1)$
		\item $p_{\text{obs}} \sim \text{Beta}(a,b)$
		\begin{itemize}
			\item $a, b \sim \text{Gamma}(1,0.1)$
			\item E similar
			\item $p$ and $E$ had restricted distributions
		\end{itemize}
		\item Burn-in period 10,000 iterations
		\item Covariates: observer, days since snow
	\end{itemize}
\end{frame}

\begin{frame}{Testing the model- data simulations}
	\begin{itemize}
		\item Simulated data with known $\psi$, $\theta$, $p$, $E$.
		\item To simplify, every observer flew every day, flights ran all 
		three days after a snow event
		\item Ran data on our model
		\item When regularity restriction lifted, similar results
	\end{itemize}
\end{frame}

\begin{frame}{Results from simulated data}
	\begin{itemize}
		\item Lower values for $\psi$ and $\theta$ had better convergence and 
		estimates
		\item 95\% confidence interval about 0.2 units wide
		\item Estimates usually within 0.1 of actual value
		\item Overall, model estimates parameters well
	\end{itemize}
\end{frame}

\begin{frame}{Modeling spatial correlation}
	\begin{itemize}
		\item Conditional autoregressive (CAR) models
		\item Allows extreme values to influence estimates for neighboring sites
		\item Placed CAR prior on $\theta$, track-laying probability
		\item With CAR model, each site has a unique estimate of $\theta$
	\end{itemize}
\end{frame}

%DNR only slide
\begin{frame}{CAR model specifics}
	\begin{itemize}
		\item $\tau^2 =$ conditional variance
		\item $(\tau^2)^{-1} \sim \text{Gamma}(0.5,0.0005)$
		\item $\text{logit}(\theta_s)=\alpha_0+\alpha_{1_s}$
		\item $\alpha_0 \sim$ Improper uniform, $\alpha_1 \sim$ Gaussian CAR
	\end{itemize}
\end{frame}

%DNR slide
\begin{frame}[label=currentslide]{Testing the CAR model}
	\begin{itemize}
		\item Simulated data with correlation in $\theta$
		\begin{itemize} 
			\item $P(\text{track in site }i|\text{no track in site }i-1)=\theta$
			\item $P(\text{track in site }i|\text{track in site }i-1)=\theta+
			\alpha$
		\end{itemize}
		\item CAR model did not converge
		\item Simulated data more independent than actual data (from $\hat{S}$)
		\item Added similar correlation in $\psi$
		\begin{itemize}
			\item Data converged more often
			\item Independence more similar to that of actual data
		\end{itemize}
	\end{itemize}
\end{frame}

%Carleton slide
\end{document}
